Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
Adding ref

The problem of estimating a risk or uncertainty measure of $Y$ has applications in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review}, robust engineering design\raft{add cites from AFOSR or EnvAI}, and algorithmic fairness\raft{Bob}.
For examples of risk measures, one may wish to estimate the upper confidence bound $\E[Y] + \lambda \Var[Y]$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.
Uncertainty measures can be unbiased versions of the above, such as the variance, or an entropy or norm of the distribution of $Y$.
Risk and uncertainty measures are typically not elicitable, so this problem falls under Quadrant 4.
\citet{frongillo2020elicitation} give prediction dimension lower bounds for a broad class of risk and uncertainty measures, namely Bayes risks.
As stated above, these bounds are with respect to identifiable properties, and bounds for convex surrogates are left as a major open question.

>>>>

The problem of estimating a risk or uncertainty measure of $Y$ has applications in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review}, robust engineering design\raft{add cites from AFOSR or EnvAI}, and algorithmic fairness~\citep{williamson2019fairness}.
For examples of risk measures, one may wish to estimate the upper confidence bound $\E[Y] + \lambda \Var[Y]$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.
Uncertainty measures can be unbiased versions of the above, such as the variance, or an entropy or norm of the distribution of $Y$.
Risk and uncertainty measures are typically not elicitable, so this problem falls under Quadrant 4.
\citet{frongillo2020elicitation} give prediction dimension lower bounds for a broad class of risk and uncertainty measures, namely Bayes risks.
As stated above, these bounds are with respect to identifiable properties, and bounds for convex surrogates are left as a major open question.
